---
title: "Lab 7"
author: "Conner Smith"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning =  FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(kableExtra)
library(GGally)
library(modelsummary)
library(stargazer)

```

# Intro to ggpairs

Use GGally::ggpairs() to create a pairs plot.

```{r}
ggpairs(penguins)

```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")

# Simpson's paradox, removing species reverses the trend (omitted variable bias)

```

# MULTIPLE LINEAR REGRESSION Penguins 

Use multiple linear regression to try and understand the relationship between multiple variable and a single continuous outcome variable (body mass).

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Return just the coefficients
penguin_lm 

```

On average, we would expect a 1 millimeter increase in flipper length to be associated with a 51.54 gram increase in body mass if all else is constant. 

Use `summary()` to get more information. 

```{r}
summary(penguin_lm)

# bill depth is only variable where coefficient is non-significant (could be zero), p-value alone not groudns for adding/removing variable from model 

# Use adjusted r squared for multiple linear models 
```
76% of variance in penguin body mass is explained by this model

# Use broom functions to clean up the outputs 

Use `broom::tidy()` for coefficient summary and `broom:glance()` for model summary as a data frame. 

```{r}
penguin_lm_tidy <- tidy(penguin_lm)

penguin_lm_glance <- glance(penguin_lm)
```

`r penguin_lm_tidy[3, "estimate"]`

`r penguin_lm_tidy$estimate[3]`

## Try another model 

We have deeply explored the data and decided that 3 most critical variables are flipper length, species, and penguin sex 

```{r}

penguin_multiple <- lm(body_mass_g ~ flipper_length_mm + sex + species, data = penguins)

penguin_multiple_tidy <- tidy(penguin_multiple)

# Female is reference, Adelie is reference --- interpret with respect to reference case 

# use `broom::augment()` to get predicted values 

augment(penguin_multiple)
```

Use plot() to look at model diagnostics 

```{r}
plot(penguin_multiple)

# First and third graphs tell us if data is homoscedastic, second reveals if residuals are normally distributed, fourth shows if any outliers are skewing the data 

```

- Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex and flipper length are reasonable predictor variables 
-diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers. 

## Make output tables 

```{r results = "asis"}
#Using modelsummary: 

modelsummary(penguin_multiple)  

# Using stargazer

stargazer(penguin_multiple, type = "html")
  
```

